Improving the Efficiency of Dislocality Constraints for an Automated Software Mapping in Safety-Critical Systems

### 2017-12-20 paper.tex
Added text for a new section to introduce dislocalities

\documentclass[english,biblatex]{lni}
\usepackage{hyperref}
\usepackage[backend=biber]{biblatex}
\addbibresource{systems-engineering.bib}
\ExecuteBibliographyOptions{}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png}
\graphicspath{{figures/}}

@@

\begin{itemize}
\item Simple Modeling approach for a CSP (location variables)
\item Use allDiffererent constraint - straight forward
\item Reality: AllDifferent for List of Lists
\item Example to describe the differences
\end{itemize}

\section{Modeling Advanced Dislocality Constraints}

>>>>

\documentclass[english,biblatex]{lni}
\usepackage{hyperref}
\usepackage[backend=biber]{biblatex}
\addbibresource{systems-engineering.bib}
\ExecuteBibliographyOptions{}
\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png}
\graphicspath{{figures/}}
\usepackage{subcaption}

@@

The semantics of a dislocality requirement can be illustrated with the following deployment problem (see Figure~\ref{example}).
In the example system, there are three \emph{applications} consisting of one or more \emph{tasks}.
Each task has to be mapped to exactly one of the \emph{processors} in the system.
It is assumed, that the processor contains multiple cores, so that multiple tasks can be mapped to a single processor.
However, in order to ensure fault tolerance, a \emph{dislocality} requirement is added for all applications.
This means, that the applications must not share a processor, so that a faulty processor affects only one application.

\begin{figure}
\centering
\subcaptionbox{Simple Case}{\includegraphics[width=0.47\textwidth]{application-mapping-simple}}%
\hfill
\subcaptionbox{Complex Case}{\includegraphics[width=0.47\textwidth]{application-mapping-complex}}%
\caption{An Example Deployment Problem - Mapping Tasks to Processors}
\label{example}
\end{figure}

Expressing the basic deployment problem with constraints is straight forward.
Each task $i$ in the system is represented by an integer variable $X_i \in \{0, 1, \dots, n-1\}$. The domain of each variable $X_i$ corresponds to the indices of the $n$ processors in the system.
This formulation is still missing the constraints for the dislocality requirements.

In the simple case, if all applications consist of only one task, this can be achieved with a single \texttt{allDifferent} constraint (see~\cite{GCCAT2014}) over all variables $X_i$.
This situation is depicted in Figure~\ref{example}~(a).
Fortunately, Choco 4 already contains an implementation for an \texttt{allDifferent} constraint based on the algorithm of Régin~\cite{Regin1994}.

However, in reality, applications usually consist of more than just one task and tasks of the same application \emph{can} typically share the same processor.
This situation is more complex and depicted in Figure~\ref{example}~(b).
Unfortunately, in this case, the previous approach of applying a single \texttt{allDifferent} constraint over all variables $X_i$ can no longer be used.
It would prevent solutions in which a processor is shared by multiple tasks of the same application.
The existing \texttt{allDifferent} constraint only ensures, that values for a list of variables are different.
However, the complex case requires an advanced \texttt{allDifferent} constraint operating with a list of a list of variables and ensuring that the combined values for each list of variables are different.
Unfortunately, such a constraint is neither part of the Global Constraint Catalog~\cite{GCCAT2014} nor available in Choco 4.

\section{Modeling Complex Dislocality Requirements}
